---
title: "bibliometric analysis"
author: "Cristiano da SIlva Santos"
date: "4/13/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Bibliographic Collection

**Data source**:   Scopus 
**Data format**:   Csv
**Query**:         (innovation OR innovate) AND ("public sector" OR "public administration" OR "public management" OR "public organisation" OR "public service") INTERSECT “Public Innovation” OR “Public Sector Innovation” OR “Government Innovation” OR “Public Service Innovation” OR “Innovation in Public Administration” OR “Innovation Management in Public Sector” OR “Public Sector Technology Innovation” OR “Government Policy Innovation” AND NOT “Government Innovation Support”
**Timespan**:      -2023
**Document Type**: Articles  
**Search fields**: Titles
**Query data**:     01/03/2024

```{r import}
library(bibliometrix)
library(akc)
library(BibPlots)
library(dplyr)
M <- convert2df("../data/raw_data/2024_scopus_public_inovation.csv", dbsource="scopus",format="csv")
M <- M[M$PY <= 2023, ]
results <- biblioAnalysis(M)
resumo <- summary(results, verbose = FALSE)

```


## Section 1: Descriptive Analysis

### Main information about data 

```{r main information, echo=TRUE, comment=NA}
tab <- resumo$MainInformationDF
tab <- tab[-1,]
rownames(tab) <- NULL
knitr::kable(tab)
```

### Most Productive Authors

```{r Most Productive Authors, echo=TRUE, comment=NA}
tab <- resumo$MostProdAuthors
knitr::kable(tab)
```

### Country Publications

```{r Country Publications, echo=TRUE, comment=NA}
tab1 <- resumo$MostProdCountries
tab2 <- resumo$TCperCountries
knitr::kable(tab1)
knitr::kable(tab2)
```

### Most Relevant Sources

```{r Most Relevant Sources, echo=TRUE, comment=NA}
tab <- resumo$MostRelSources
knitr::kable(tab)
```



### keyword co-occurrence
```{r keyword co-occurrence, echo=TRUE, comment=NA}
M %>% 
  keyword_clean(id = "DI",
  keyword = "DE",
  sep = ";",
 ) -> clean_data
#Merge keywords that have common stem or lemma, and return the majority form of the word
clean_data %>% 
  keyword_merge() -> merged_data


merged_data %>% 
  keyword_group(min_freq = 2) -> grouped_data

grouped_data %>% 
  keyword_vis()
```





